Automated topic naming to support analysis of software maintenance activities

### 2010-08-18 icse/icse2011.tex
Made that table finally work. So Sloppy.
ANyways check_validate.py now produces yes_no reports which count things for you
Updated the table again with new data from lda_relator

%\todo[inline,color=green]{this table should have mysql}
\begin{table}
% This data came from running  
%   python check_validity.py
%  in src/validate
% and then running
% tail -n 5 *maxdb*yes_no*
% tail -n 5 *mysql*yes_no*
	\centering
\begin{tabular}{c|c|c|c}
\toprule
Project & Measure & \textsf{exp1} & \textsf{exp2} & \textsf{exp3} \\
\midrule
%Named topics   & 281 & 125 & 328  \\
%Unnamed topics & 139 & 295 & 92   \\
MaxDB 7.500 & Named Topics   & 305 & 183 & 330 \\
MaxDB 7.500 & Unnamed Topics & 84  & 206 & 59   \\
MaxDB 7.500 & Total  Topics  & 389 & 389 & 389 \\
MySQL 3.23  & Named Topics   & 341 & 202 & 469 \\
MySQL 3.23  & Unnamed Topics & 245 & 384 & 117 \\
MySQL 3.23  & Total  Topics  & 586 & 586 & 586 \\
\bottomrule
\end{tabular}
	\caption{Automatic topic labelling for MaxDB 7.500}
	\label{tbl:wordlist}

>>>>

%\todo[inline,color=green]{this table should have mysql}
\begin{table}

% % This data came from running  
% %   python check_validity.py
% %  in src/validate
% % and then running
% % tail -n 5 *maxdb*yes_no*
% % tail -n 5 *mysql*yes_no*
% ok the new way is to run lda_relator
% src/validate/lda_relator_counts.sh
	\centering
\begin{tabular}{l|c|c|c|c}
\toprule
Project & Measure & \textsf{exp1} & \textsf{exp2} & \textsf{exp3} \\
\midrule
% NOTE THESE WERE THE OLD VALUES
% WHY DID THEY CHANGE???
% DUNNO
%Named topics   & 281 & 125 & 328  \\
%Unnamed topics & 139 & 295 & 92   \\

% these were check_validate
% MaxDB 7.500 & Named Topics   & 305 & 183 & 330 \\
% MaxDB 7.500 & Unnamed Topics & 84  & 206 & 59   \\
% MaxDB 7.500 & Total  Topics  & 389 & 389 & 389 \\
% MySQL 3.23  & Named Topics   & 341 & 202 & 469 \\
% MySQL 3.23  & Unnamed Topics & 245 & 384 & 117 \\
% MySQL 3.23  & Total  Topics  & 586 & 586 & 586 \\

% these are lda relator

MaxDB 7.500 & Named Topics   & 281 & 125 & 328 \\ % these numbers are
                                % slightly different solely because
                                % we're counting empty topics
                                % maxdb has 80 empty topics
MaxDB 7.500 & Unnamed Topics & 219  & 375 &  172  \\
MaxDB 7.500 & Total  Topics  & 500 & 500 & 500 \\
MySQL 3.23  & Named Topics   & 524 & 273 & 773 \\
MySQL 3.23  & Unnamed Topics & 476 & 727 & 227 \\
MySQL 3.23  & Total  Topics  & 1000 & 1000 & 1000 \\

\bottomrule
\end{tabular}
	\caption{Automatic topic labelling for MaxDB 7.500}
	\label{tbl:wordlist}
